---
  title: "QC Record: Andrew test milestone"
  subtitle: "Git repository: ghqc_status_project2"
  author: wescummings
  date: September 17, 2025
  header-includes:
  - \usepackage{float}
  - \usepackage{longtable}
  - \usepackage{booktabs}
  - \usepackage{makecell}
  - \usepackage{graphicx}
  - \usepackage{array}
  - \usepackage{fancyhdr}
  - \usepackage{xcolor}
  - \pagestyle{fancy}
  - \newcolumntype{R}[1]{>{\raggedright\arraybackslash}p{#1}}
  - \setlength{\headheight}{30pt}
  - \fancyfoot[C]{Page \thepage\ of \pageref{LastPage}}
  - \usepackage{lastpage}
  - \usepackage{microtype}
  - \usepackage{ragged2e}
  - \usepackage{fvextra}
  - \usepackage[normalem]{ulem}
  - \justifying
  - \sloppy
  - \lstset{breaklines=true}
  - \fancyhead[R]{\includegraphics[width=2cm, height=1.5cm, keepaspectratio]{~/.local/share/ghqc/ghqc.a2ai/logo.png}}
  - \fancyhead[C]{}
  - \fancyhead[L]{}
  - "\\fancypagestyle{plain}{"
  - "\\renewcommand{\\headrulewidth}{0.4pt}"
  - "}"
  output:
    pdf_document:
      latex_engine: xelatex
      extra_dependencies: ["xcolor"]
      pandoc_args: --listings
      toc: true
      toc_depth: 2
---

  \newpage
```{r setup, include=FALSE}
  library(knitr)
  library(dplyr)
  library(kableExtra)
  knitr::opts_chunk$set(eval=FALSE, warning = FALSE)
```

```{r, include=FALSE, eval=TRUE}
milestone_df <- read.csv("/var/folders/n_/p8p3xyjn17j46vzr511810900000gn/T//RtmpqpwUoo/file8f8f1d9f54d5.csv")


milestone_df <- milestone_df %>%
mutate(across(everything(), ~ ifelse(is.na(.), "NA", .)))
invisible(milestone_df)
```

# Milestone Summary
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}

table <- milestone_df %>%
knitr::kable(
  col.names = c("Title", "Description", "Status", "Issues"),
  format = "latex",
  booktabs = TRUE,
  escape = FALSE,
  longtable = TRUE,
  linesep = "\\addlinespace\\addlinespace"
) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  footnote(general=c("\\\\textcolor{red}{U} Unapproved Issue", "\\\\textcolor{red}{C} Issue with unchecked items"), general_title = "", escape = FALSE) %>%
  column_spec(1, width = "0.20\\\\textwidth", latex_valign = "p") %>%
  column_spec(2, width = "0.20\\\\textwidth", latex_valign = "p") %>%
  column_spec(4, width = "0.43\\\\textwidth", latex_valign = "p")
```

```{r, echo=FALSE, eval=TRUE, results='asis'}
print(table)
```

\newpage
# Andrew test milestone


```{r, include=FALSE, eval=TRUE}
summary_df <- read.csv("/var/folders/n_/p8p3xyjn17j46vzr511810900000gn/T//RtmpqpwUoo/file8f8f477a7b24.csv")


summary_df <- summary_df %>%
mutate(across(everything(), ~ ifelse(is.na(.), "NA", .)))
invisible(summary_df)
```

## **Issue Summary**
```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
table <- summary_df %>%

knitr::kable(
  col.names = c("File Path", "QC Status", "Author", "QCer", "Issue Closer"),
  format = "latex",
  booktabs = TRUE,
  escape = TRUE,
  longtable = TRUE,
  linesep = "\\addlinespace\\addlinespace"
) %>%
  kable_styling(latex_options = c("repeat_header")) %>%
  column_spec(1, width = "10em") %>%
  column_spec(2, width = "7em") %>%
  column_spec(3, width = "10em")
```

```{r, echo=FALSE, eval=TRUE, results='asis'}
print(table)
```

\newpage
## scripts/_baseline-deps.R

### Issue Information

* **Issue number:** 28

* **Issue creator:** Andrew-Acker125 at 2025-09-08 17:57:47

* **QCer:** No QCer

* **QC status:** Awaiting approval

* **Git status:** View on QC branch: <em>archive_testing</em>

* **Initial QC commit:** 8de9a34e6f595f6b2d13a82f2b439c23c7b8deb0

* **Last QC commit:** 8de9a34e6f595f6b2d13a82f2b439c23c7b8deb0

* **Issue URL:** https://github.com/A2-ai/ghqc_status_project2/issues/28

* **Issue state:** Open

* **Milestone:** Andrew test milestone

### Issue Body


**Metadata**


* initial qc commit: 8de9a34e6f595f6b2d13a82f2b439c23c7b8deb0
* git branch: [archive_testing](https://github.com/A2-ai/ghqc_status_project2/tree/8de9a34e6f595f6b2d13a82f2b439c23c7b8deb0)
* author: jenna-a2ai <jenna@a2-ai.com>
* <a href="https://github.com/A2-ai/ghqc_status_project2/blob/8de9a3/scripts/_baseline-deps.R" target="_blank">file contents at initial qc commit</a>


**Relevant files**

- **rv.lock**
   - [`rv.lock`](https://github.com/A2-ai/ghqc_status_project2/blob/archive_testing/rv.lock)
&nbsp;
- **lefthook.yml**
   - [`lefthook.yml`](https://github.com/A2-ai/ghqc_status_project2/blob/archive_testing/lefthook.yml)


**Data Assembly**


**Clockify code**: [INSERT]

**QC review due date**: [INSERT]



**Reproducibility and Organization**

- [ ] Script is a quarto document
- [ ] Script renders free of error within the Rproject space
- [ ] `.rv$summary()` present at beginning of script and passes
- [ ] Relative paths are used
- [ ] `.Rprofile` is present in same directory as final script
- [ ] Parquet files are used where available
Files that should be parquet:
    - [INSERT]
- [ ] Data hash codes are printed and match source and output data
Expected hash files: 
    - [INSERT]
- [ ] Correct source data files are read in
Correct source data: 
    - [INSERT]
- [ ] Final dataset outputs to expected location as a csv, converts all NA values to a period, and outputs a hash
- [ ] All code chunks are labeled
- [ ] `sessioninfo()` included at the conclusion of script

**yspec**

- [ ] All yspec files can be found in `<project>/data/derived` and are excluded from the gitignore
- [ ] All variables have descriptions. All descriptions are easy to read and understand. All variables have units where applicable
- [ ] All categorical variables have all options outlined and a 1:1 numerical decoded value. All categorical variables match the decoding present in the yspec
- [ ] All continuous variables specify units and all units match those of the final dataset. If multiple analytes are included in a single column, units are clear for each analyte
- [ ] The yspec file contains all necessary variables for analysis, including both project specific variables and NONMEM required variables

**Dataset Assumptions - Automated**
These can be done using pointblank and QCer can just confirm these pass!

- [ ] List pointblank assumptions:
    - [INSERT]
- [ ] The final dataset includes both a numeric (ID) and character (e.g. USUBJID) version of the unique subject identifier
- [ ] The final dataset includes all columns listed in the corresponding yspec file
- [ ] Any missing columns or observations are confirmed to be missing in source data and marked as -999
- [ ] Missing data is documented appropriately in dataset

**Data Assumptions - Manual**
These **can't** be done using pointblank and QCer must look closely at specific sections of code

- [ ] All manual conversions are accurate and consistent
- [ ] All manual imputations are well documented to outside sources or sufficiently justified
- [ ] All manual imputations are accurate according to their specified source
- [ ] All assumptions are well justified (e.g. by the protocol, project lead decision, client decision, etc.), documented, and reasonable
- [ ] All records to be excluded (e.g. for all analyses, for sensitivity analysis only) are properly identified, justified, and documented (i.e., CFLAG or other flag column)

**Misc**

- [ ] Code is easily readable and follows general coding guidelines [(link to code hub)](https://a2-ai.atlassian.net/wiki/spaces/KB/pages/78872577/Code+Hub)
- [ ] Helper functions are well documented, make sense, make reasonable assumptions, and follow good coding practices
- [ ] Helper function arguments match as stated in yspec (e.g. SEX variable in Cockcroft-Gault equation matches decoding in yspec)

### Comments



### Events

- milestone set to Andrew test milestone by Andrew-Acker125 at 2025-09-08 17:57:48

- labeled by Andrew-Acker125 at 2025-09-08 17:57:48

- labeled by Andrew-Acker125 at 2025-09-08 17:57:48

- labeled by Andrew-Acker125 at 2025-09-08 17:57:49


### Detailed Timeline

- milestone set to Andrew test milestone by Andrew-Acker125 at 2025-09-08 17:57:48

- labeled by Andrew-Acker125 at 2025-09-08 17:57:48

- labeled by Andrew-Acker125 at 2025-09-08 17:57:48

- labeled by Andrew-Acker125 at 2025-09-08 17:57:49




\newpage


\newpage
## scripts/file_d.R

### Issue Information

* **Issue number:** 27

* **Issue creator:** Andrew-Acker125 at 2025-09-08 16:03:47

* **QCer:** No QCer

* **QC status:** Awaiting approval

* **Git status:** View on QC branch: <em>archive_testing</em>

* **Initial QC commit:** 8de9a34e6f595f6b2d13a82f2b439c23c7b8deb0

* **Last QC commit:** 8de9a34e6f595f6b2d13a82f2b439c23c7b8deb0

* **Issue URL:** https://github.com/A2-ai/ghqc_status_project2/issues/27

* **Issue state:** Open

* **Milestone:** Andrew test milestone

### Issue Body


**Metadata**


* initial qc commit: 8de9a34e6f595f6b2d13a82f2b439c23c7b8deb0
* git branch: [archive_testing](https://github.com/A2-ai/ghqc_status_project2/tree/8de9a34e6f595f6b2d13a82f2b439c23c7b8deb0)
* author: Jenna Johnson <jenna@a2-ai.com>
* <a href="https://github.com/A2-ai/ghqc_status_project2/blob/8de9a3/scripts/file_d.R" target="_blank">file contents at initial qc commit</a>


**Relevant files**

- **rproject.toml**
   - [`rproject.toml`](https://github.com/A2-ai/ghqc_status_project2/blob/archive_testing/rproject.toml)


**Data Assembly**


**Clockify code**: [INSERT]

**QC review due date**: [INSERT]



**Reproducibility and Organization**

- [ ] Script is a quarto document
- [ ] Script renders free of error within the Rproject space
- [ ] `.rv$summary()` present at beginning of script and passes
- [ ] Relative paths are used
- [ ] `.Rprofile` is present in same directory as final script
- [ ] Parquet files are used where available
Files that should be parquet:
    - [INSERT]
- [ ] Data hash codes are printed and match source and output data
Expected hash files: 
    - [INSERT]
- [ ] Correct source data files are read in
Correct source data: 
    - [INSERT]
- [ ] Final dataset outputs to expected location as a csv, converts all NA values to a period, and outputs a hash
- [ ] All code chunks are labeled
- [ ] `sessioninfo()` included at the conclusion of script

**yspec**

- [ ] All yspec files can be found in `<project>/data/derived` and are excluded from the gitignore
- [ ] All variables have descriptions. All descriptions are easy to read and understand. All variables have units where applicable
- [ ] All categorical variables have all options outlined and a 1:1 numerical decoded value. All categorical variables match the decoding present in the yspec
- [ ] All continuous variables specify units and all units match those of the final dataset. If multiple analytes are included in a single column, units are clear for each analyte
- [ ] The yspec file contains all necessary variables for analysis, including both project specific variables and NONMEM required variables

**Dataset Assumptions - Automated**
These can be done using pointblank and QCer can just confirm these pass!

- [ ] List pointblank assumptions:
    - [INSERT]
- [ ] The final dataset includes both a numeric (ID) and character (e.g. USUBJID) version of the unique subject identifier
- [ ] The final dataset includes all columns listed in the corresponding yspec file
- [ ] Any missing columns or observations are confirmed to be missing in source data and marked as -999
- [ ] Missing data is documented appropriately in dataset

**Data Assumptions - Manual**
These **can't** be done using pointblank and QCer must look closely at specific sections of code

- [ ] All manual conversions are accurate and consistent
- [ ] All manual imputations are well documented to outside sources or sufficiently justified
- [ ] All manual imputations are accurate according to their specified source
- [ ] All assumptions are well justified (e.g. by the protocol, project lead decision, client decision, etc.), documented, and reasonable
- [ ] All records to be excluded (e.g. for all analyses, for sensitivity analysis only) are properly identified, justified, and documented (i.e., CFLAG or other flag column)

**Misc**

- [ ] Code is easily readable and follows general coding guidelines [(link to code hub)](https://a2-ai.atlassian.net/wiki/spaces/KB/pages/78872577/Code+Hub)
- [ ] Helper functions are well documented, make sense, make reasonable assumptions, and follow good coding practices
- [ ] Helper function arguments match as stated in yspec (e.g. SEX variable in Cockcroft-Gault equation matches decoding in yspec)

### Comments



### Events

- milestone set to Andrew test milestone by Andrew-Acker125 at 2025-09-08 16:03:47

- labeled by Andrew-Acker125 at 2025-09-08 16:03:48

- labeled by Andrew-Acker125 at 2025-09-08 16:03:48

- labeled by Andrew-Acker125 at 2025-09-08 16:03:49


### Detailed Timeline

- milestone set to Andrew test milestone by Andrew-Acker125 at 2025-09-08 16:03:47

- labeled by Andrew-Acker125 at 2025-09-08 16:03:48

- labeled by Andrew-Acker125 at 2025-09-08 16:03:48

- labeled by Andrew-Acker125 at 2025-09-08 16:03:49




\newpage


\newpage
## scripts/file_e.R

### Issue Information

* **Issue number:** 26

* **Issue creator:** Andrew-Acker125 at 2025-09-04 14:43:22

* **QCer:** No QCer

* **QC status:** Awaiting approval

* **Git status:** View on QC branch: <em>archive_testing</em>

* **Initial QC commit:** 09c3c57072eac352c9faafd765b48b211e60d702

* **Last QC commit:** 09c3c57072eac352c9faafd765b48b211e60d702

* **Issue URL:** https://github.com/A2-ai/ghqc_status_project2/issues/26

* **Issue state:** Open

* **Milestone:** Andrew test milestone

### Issue Body


**Metadata**


* initial qc commit: 09c3c57072eac352c9faafd765b48b211e60d702
* git branch: [archive_testing](https://github.com/A2-ai/ghqc_status_project2/tree/09c3c57072eac352c9faafd765b48b211e60d702)
* author: Jenna Johnson <jenna@a2-ai.com>
* <a href="https://github.com/A2-ai/ghqc_status_project2/blob/09c3c5/scripts/file_e.R" target="_blank">file contents at initial qc commit</a>



**Data Assembly**


**Clockify code**: [INSERT]

**QC review due date**: [INSERT]



**Reproducibility and Organization**

- [ ] Script is a quarto document
- [ ] Script renders free of error within the Rproject space
- [ ] `.rv$summary()` present at beginning of script and passes
- [ ] Relative paths are used
- [ ] `.Rprofile` is present in same directory as final script
- [ ] Parquet files are used where available
Files that should be parquet:
    - [INSERT]
- [ ] Data hash codes are printed and match source and output data
Expected hash files: 
    - [INSERT]
- [ ] Correct source data files are read in
Correct source data: 
    - [INSERT]
- [ ] Final dataset outputs to expected location as a csv, converts all NA values to a period, and outputs a hash
- [ ] All code chunks are labeled
- [ ] `sessioninfo()` included at the conclusion of script

**yspec**

- [ ] All yspec files can be found in `<project>/data/derived` and are excluded from the gitignore
- [ ] All variables have descriptions. All descriptions are easy to read and understand. All variables have units where applicable
- [ ] All categorical variables have all options outlined and a 1:1 numerical decoded value. All categorical variables match the decoding present in the yspec
- [ ] All continuous variables specify units and all units match those of the final dataset. If multiple analytes are included in a single column, units are clear for each analyte
- [ ] The yspec file contains all necessary variables for analysis, including both project specific variables and NONMEM required variables

**Dataset Assumptions - Automated**
These can be done using pointblank and QCer can just confirm these pass!

- [ ] List pointblank assumptions:
    - [INSERT]
- [ ] The final dataset includes both a numeric (ID) and character (e.g. USUBJID) version of the unique subject identifier
- [ ] The final dataset includes all columns listed in the corresponding yspec file
- [ ] Any missing columns or observations are confirmed to be missing in source data and marked as -999
- [ ] Missing data is documented appropriately in dataset

**Data Assumptions - Manual**
These **can't** be done using pointblank and QCer must look closely at specific sections of code

- [ ] All manual conversions are accurate and consistent
- [ ] All manual imputations are well documented to outside sources or sufficiently justified
- [ ] All manual imputations are accurate according to their specified source
- [ ] All assumptions are well justified (e.g. by the protocol, project lead decision, client decision, etc.), documented, and reasonable
- [ ] All records to be excluded (e.g. for all analyses, for sensitivity analysis only) are properly identified, justified, and documented (i.e., CFLAG or other flag column)

**Misc**

- [ ] Code is easily readable and follows general coding guidelines [(link to code hub)](https://a2-ai.atlassian.net/wiki/spaces/KB/pages/78872577/Code+Hub)
- [ ] Helper functions are well documented, make sense, make reasonable assumptions, and follow good coding practices
- [ ] Helper function arguments match as stated in yspec (e.g. SEX variable in Cockcroft-Gault equation matches decoding in yspec)

### Comments



### Events

- milestone set to Andrew test milestone by Andrew-Acker125 at 2025-09-04 14:43:22

- labeled by Andrew-Acker125 at 2025-09-04 14:43:23

- labeled by Andrew-Acker125 at 2025-09-04 14:43:23

- labeled by Andrew-Acker125 at 2025-09-04 14:43:24


### Detailed Timeline

- milestone set to Andrew test milestone by Andrew-Acker125 at 2025-09-04 14:43:22

- labeled by Andrew-Acker125 at 2025-09-04 14:43:23

- labeled by Andrew-Acker125 at 2025-09-04 14:43:23

- labeled by Andrew-Acker125 at 2025-09-04 14:43:24




\newpage


\newpage
## scripts/file_c.R

### Issue Information

* **Issue number:** 25

* **Issue creator:** Andrew-Acker125 at 2025-09-04 14:17:06

* **QCer:** No QCer

* **QC status:** Approved

* **Git status:** View on QC branch: <em>archive_testing</em>

* **Initial QC commit:** 09c3c57072eac352c9faafd765b48b211e60d702

* **Last QC commit:** 09c3c57072eac352c9faafd765b48b211e60d702

* **Issue URL:** https://github.com/A2-ai/ghqc_status_project2/issues/25

* **Issue state:** Closed

* **Closed by:** Andrew-Acker125

* **Closed at:** 2025-09-04 14:20:31

* **Milestone:** Andrew test milestone

### Issue Body


**Metadata**


* initial qc commit: 09c3c57072eac352c9faafd765b48b211e60d702
* git branch: [archive_testing](https://github.com/A2-ai/ghqc_status_project2/tree/09c3c57072eac352c9faafd765b48b211e60d702)
* author: jenna-a2ai <jenna@a2-ai.com>
* <a href="https://github.com/A2-ai/ghqc_status_project2/blob/09c3c5/scripts/file_c.R" target="_blank">file contents at initial qc commit</a>



**Data Assembly**


**Clockify code**: [INSERT]

**QC review due date**: [INSERT]



**Reproducibility and Organization**

- [ ] Script is a quarto document
- [ ] Script renders free of error within the Rproject space
- [ ] `.rv$summary()` present at beginning of script and passes
- [ ] Relative paths are used
- [ ] `.Rprofile` is present in same directory as final script
- [ ] Parquet files are used where available
Files that should be parquet:
    - [INSERT]
- [ ] Data hash codes are printed and match source and output data
Expected hash files: 
    - [INSERT]
- [ ] Correct source data files are read in
Correct source data: 
    - [INSERT]
- [ ] Final dataset outputs to expected location as a csv, converts all NA values to a period, and outputs a hash
- [ ] All code chunks are labeled
- [ ] `sessioninfo()` included at the conclusion of script

**yspec**

- [ ] All yspec files can be found in `<project>/data/derived` and are excluded from the gitignore
- [ ] All variables have descriptions. All descriptions are easy to read and understand. All variables have units where applicable
- [ ] All categorical variables have all options outlined and a 1:1 numerical decoded value. All categorical variables match the decoding present in the yspec
- [ ] All continuous variables specify units and all units match those of the final dataset. If multiple analytes are included in a single column, units are clear for each analyte
- [ ] The yspec file contains all necessary variables for analysis, including both project specific variables and NONMEM required variables

**Dataset Assumptions - Automated**
These can be done using pointblank and QCer can just confirm these pass!

- [ ] List pointblank assumptions:
    - [INSERT]
- [ ] The final dataset includes both a numeric (ID) and character (e.g. USUBJID) version of the unique subject identifier
- [ ] The final dataset includes all columns listed in the corresponding yspec file
- [ ] Any missing columns or observations are confirmed to be missing in source data and marked as -999
- [ ] Missing data is documented appropriately in dataset

**Data Assumptions - Manual**
These **can't** be done using pointblank and QCer must look closely at specific sections of code

- [ ] All manual conversions are accurate and consistent
- [ ] All manual imputations are well documented to outside sources or sufficiently justified
- [ ] All manual imputations are accurate according to their specified source
- [ ] All assumptions are well justified (e.g. by the protocol, project lead decision, client decision, etc.), documented, and reasonable
- [ ] All records to be excluded (e.g. for all analyses, for sensitivity analysis only) are properly identified, justified, and documented (i.e., CFLAG or other flag column)

**Misc**

- [ ] Code is easily readable and follows general coding guidelines [(link to code hub)](https://a2-ai.atlassian.net/wiki/spaces/KB/pages/78872577/Code+Hub)
- [ ] Helper functions are well documented, make sense, make reasonable assumptions, and follow good coding practices
- [ ] Helper function arguments match as stated in yspec (e.g. SEX variable in Cockcroft-Gault equation matches decoding in yspec)

### Comments

**Comment by Andrew-Acker125 at 2025-09-04 14:30:14:**

**# QC Approved**







**Metadata**


* approved qc commit: 09c3c57072eac352c9faafd765b48b211e60d702
* <a href="https://github.com/A2-ai/ghqc_status_project2/blob/09c3c5/scripts/file_c.R" target="_blank">file contents at approved qc commit</a>
* <a href="https://github.com/A2-ai/ghqc_status_project2/compare/09c3c57072eac352c9faafd765b48b211e60d702..09c3c57072eac352c9faafd765b48b211e60d702" target="_blank">initial qc commit vs. approved qc commit</a>




### Events

- milestone set to Andrew test milestone by Andrew-Acker125 at 2025-09-04 14:17:06

- labeled by Andrew-Acker125 at 2025-09-04 14:17:06

- labeled by Andrew-Acker125 at 2025-09-04 14:17:06

- labeled by Andrew-Acker125 at 2025-09-04 14:17:07

- closed by Andrew-Acker125 at 2025-09-04 14:20:31


### Detailed Timeline

- milestone set to Andrew test milestone by Andrew-Acker125 at 2025-09-04 14:17:06

- labeled by Andrew-Acker125 at 2025-09-04 14:17:06

- labeled by Andrew-Acker125 at 2025-09-04 14:17:06

- labeled by Andrew-Acker125 at 2025-09-04 14:17:07

- closed by Andrew-Acker125 at 2025-09-04 14:20:31

- commented by Andrew-Acker125 at 2025-09-04 14:30:14




\newpage


\newpage
## scripts/andrew_test_file.R

### Issue Information

* **Issue number:** 24

* **Issue creator:** Andrew-Acker125 at 2025-09-04 14:17:04

* **QCer:** No QCer

* **QC status:** Approved; subsequent file changes

* **Git status:** View on QC branch: <em>archive_testing</em>

* **Initial QC commit:** 09c3c57072eac352c9faafd765b48b211e60d702

* **Last QC commit:** 09c3c57072eac352c9faafd765b48b211e60d702

* **Issue URL:** https://github.com/A2-ai/ghqc_status_project2/issues/24

* **Issue state:** Closed

* **Closed by:** Andrew-Acker125

* **Closed at:** 2025-09-04 14:39:47

* **Milestone:** Andrew test milestone

### Issue Body


**Metadata**


* initial qc commit: 09c3c57072eac352c9faafd765b48b211e60d702
* git branch: [archive_testing](https://github.com/A2-ai/ghqc_status_project2/tree/09c3c57072eac352c9faafd765b48b211e60d702)
* author: Andrew Acker <andrew@a2-ai.com>
* <a href="https://github.com/A2-ai/ghqc_status_project2/blob/09c3c5/scripts/andrew_test_file.R" target="_blank">file contents at initial qc commit</a>


**Relevant files**

- **helper.R**
   - [`scripts/helper.R`](https://github.com/A2-ai/ghqc_status_project2/blob/archive_testing/scripts/helper.R)


**Data Assembly**


**Clockify code**: [INSERT]

**QC review due date**: [INSERT]



**Reproducibility and Organization**

- [ ] Script is a quarto document
- [ ] Script renders free of error within the Rproject space
- [ ] `.rv$summary()` present at beginning of script and passes
- [ ] Relative paths are used
- [ ] `.Rprofile` is present in same directory as final script
- [ ] Parquet files are used where available
Files that should be parquet:
    - [INSERT]
- [ ] Data hash codes are printed and match source and output data
Expected hash files: 
    - [INSERT]
- [ ] Correct source data files are read in
Correct source data: 
    - [INSERT]
- [ ] Final dataset outputs to expected location as a csv, converts all NA values to a period, and outputs a hash
- [ ] All code chunks are labeled
- [ ] `sessioninfo()` included at the conclusion of script

**yspec**

- [ ] All yspec files can be found in `<project>/data/derived` and are excluded from the gitignore
- [ ] All variables have descriptions. All descriptions are easy to read and understand. All variables have units where applicable
- [ ] All categorical variables have all options outlined and a 1:1 numerical decoded value. All categorical variables match the decoding present in the yspec
- [ ] All continuous variables specify units and all units match those of the final dataset. If multiple analytes are included in a single column, units are clear for each analyte
- [ ] The yspec file contains all necessary variables for analysis, including both project specific variables and NONMEM required variables

**Dataset Assumptions - Automated**
These can be done using pointblank and QCer can just confirm these pass!

- [ ] List pointblank assumptions:
    - [INSERT]
- [ ] The final dataset includes both a numeric (ID) and character (e.g. USUBJID) version of the unique subject identifier
- [ ] The final dataset includes all columns listed in the corresponding yspec file
- [ ] Any missing columns or observations are confirmed to be missing in source data and marked as -999
- [ ] Missing data is documented appropriately in dataset

**Data Assumptions - Manual**
These **can't** be done using pointblank and QCer must look closely at specific sections of code

- [ ] All manual conversions are accurate and consistent
- [ ] All manual imputations are well documented to outside sources or sufficiently justified
- [ ] All manual imputations are accurate according to their specified source
- [ ] All assumptions are well justified (e.g. by the protocol, project lead decision, client decision, etc.), documented, and reasonable
- [ ] All records to be excluded (e.g. for all analyses, for sensitivity analysis only) are properly identified, justified, and documented (i.e., CFLAG or other flag column)

**Misc**

- [ ] Code is easily readable and follows general coding guidelines [(link to code hub)](https://a2-ai.atlassian.net/wiki/spaces/KB/pages/78872577/Code+Hub)
- [ ] Helper functions are well documented, make sense, make reasonable assumptions, and follow good coding practices
- [ ] Helper function arguments match as stated in yspec (e.g. SEX variable in Cockcroft-Gault equation matches decoding in yspec)

### Comments

**Comment by Andrew-Acker125 at 2025-09-04 14:30:23:**

**# QC Approved**







**Metadata**


* approved qc commit: 09c3c57072eac352c9faafd765b48b211e60d702
* <a href="https://github.com/A2-ai/ghqc_status_project2/blob/09c3c5/scripts/andrew_test_file.R" target="_blank">file contents at approved qc commit</a>
* <a href="https://github.com/A2-ai/ghqc_status_project2/compare/09c3c57072eac352c9faafd765b48b211e60d702..09c3c57072eac352c9faafd765b48b211e60d702" target="_blank">initial qc commit vs. approved qc commit</a>




### Events

- milestone set to Andrew test milestone by Andrew-Acker125 at 2025-09-04 14:17:04

- labeled by Andrew-Acker125 at 2025-09-04 14:17:05

- labeled by Andrew-Acker125 at 2025-09-04 14:17:05

- closed by Andrew-Acker125 at 2025-09-04 14:18:38

- reopened by Andrew-Acker125 at 2025-09-04 14:39:43

- closed by Andrew-Acker125 at 2025-09-04 14:39:47


### Detailed Timeline

- milestone set to Andrew test milestone by Andrew-Acker125 at 2025-09-04 14:17:04

- labeled by Andrew-Acker125 at 2025-09-04 14:17:05

- labeled by Andrew-Acker125 at 2025-09-04 14:17:05

- closed by Andrew-Acker125 at 2025-09-04 14:18:38

- commented by Andrew-Acker125 at 2025-09-04 14:30:23

- reopened by Andrew-Acker125 at 2025-09-04 14:39:43

- closed by Andrew-Acker125 at 2025-09-04 14:39:47




\newpage



\newpage


